% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% test.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[a4paper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Bohong ZHAO}
\newcommand{\CVTitle}{Bohong ZHAO's CV}
\newcommand{\CVNote}{CV compiled on {\today}, check it on \href{https://github.com/hackroid/cv}{github.com/hackroid/cv}, branch: job}
\newcommand{\CVWebpage}{https://github.com/hackroid/blob/main/CV_BohongZHAO.pdf}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}
\DeclareSymbolFont{extraup}{U}{zavm}{m}{n}
\DeclareMathSymbol{\varheart}{\mathalpha}{extraup}{86}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
    \href{http://www.naist.jp/en/}
    {Postgraduate | Nara Institute of Science and Technology}
    \par
    zhao.bohong.yx7[at]is.naist.jp
    \,\SubBulletSymbol\,
    +81\,(90)\,8863-1652
    \,\SubBulletSymbol\,
    \href{https://github.com/hackroid/}{github.com/hackroid}
    \,\SubBulletSymbol\,
    \href{https://www.linkedin.com/in/%E5%8D%9A%E5%BC%98-%E8%B5%B5-b7ab09136/}{LinkedIn}
    \,\SubBulletSymbol\,
    \href{https://hackroid.com}{blog}
\end{SubTitle}

\begin{Body}

    %%%%%%%%%%%%%%%
    %% EDUCATION %%
    %%%%%%%%%%%%%%%

    \Section
    {Education}
    {Education}
    {PDF:Education}

    \Entry
    \href{http://www.naist.jp/en/}
    {\textbf{Nara Institute of Science and Technology (NAIST)}},
    Ikoma, Nara, Japan
    \Gap
    \BulletItem
    Master Program in
    \href{http://isw3.naist.jp/home-en.html}
    {Information Science}
    \hfill
    \DatestampYMD{2022}{04}{01} --
    \DatestampYMD{2024}{04}{01} (expected)
    \begin{Detail}
        \SubBulletItem
        Supervisor: \href{http://icb-lab.naist.jp/members/yoshi/index.html}{Prof. Yoshinobu Sato}, \href{http://icb-lab.naist.jp/index.html}{Imaging-based Computational Biomedicine Lab}
    \end{Detail}

    \Gap

    \Entry
    \href{https://www.ubc.ca/}
    {\textbf{The University of British Columbia (UBC)}},
    Vancouver, BC, Canada
    \hfill
    \DatestampYMD{2018}{07}{15} --
    \DatestampYMD{2018}{08}{15}
    %\Gap
    \BulletItem
    Summer Program: Algorithms \& Webapp Courses

    %\BigGap
    \Gap

    \Entry
    \href{https://www.sustech.edu.cn/}
    {\textbf{Southern University of Science and Technology (SUSTech)}},
    Shenzhen, Guangdong, China
    \Gap
    \BulletItem
    B.Eng. in
    \href{http://cse.sustech.edu.cn/}
    {Computer Science and Engineering}
    \hfill
    \DatestampYMD{2016}{09}{01} --
    \DatestampYMD{2021}{07}{01}
    \begin{Detail}
        \SubBulletItem
        Relavent courses:
        Data Structures and Algorithms Analysis,
        Discrete Mathematics,
        Digital Logic,
        Computer System Design and Application,
        Computer Organization Principle,
        Database Principle,
        Probability and Statistics,
        Artificial Intelligence,
        Computer Networks,
        Embedded System and Microcomputer Principle,
        Object-oriented Analysis and Design,
        Software Engineering,
        C/C++ Programming Design,
        Computer Vision,
        Introduction to Cognitive Science,
        Operating System,
        Robotics,
        Introduction to Big Data Analysis
    \end{Detail}

    %%%%%%%%%%%%%%%%%%%%%%%%%
    %% RESEARCH EXPERIENCE %%
    %%%%%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Research Experience}
    {Research Experience}
    {PDF:ResearchExperience}

    % \Gap
    \Entry
    \textbf{2D/3D Registration using Deep Learning}
    %\Gap
    \BulletItem
    Master Research Theme, NAIST, Supervisor: \href{http://icb-lab.naist.jp/members/yoshi/index.html}{Prof. Yoshinobu Sato}
    \hfill
    \DatestampYMD{2022}{04}{01} -- Present
    % \DatestampYMD{2019}{09}{01}
    \begin{Detail}
        \SubBulletItem
        Languages \& Framework: Python, PyTorch, MATLAB
        \SubBulletItem
        Summary:
        Implementing deep learning methods to 2D/3D registration.
    \end{Detail}

    \Entry
    \href{https://github.com/hackroid/cv-xmp}
    {\textbf{Medical Image Processing using Deep Learning} [link to GitHub]}
    %\Gap
    \BulletItem
    Summer Research Project, SUSTech, Supervisor: \href{https://faculty.sustech.edu.cn/fengzheng/en/}{Prof.~Feng~Zheng}
    \hfill
    \DatestampYMD{2019}{06}{01} --
    \DatestampYMD{2019}{09}{01}
    \begin{Detail}
        \SubBulletItem
        Languages \& Framework: Python, PyTorch
        \SubBulletItem
        Summary:
        An elementary deep learning research training, applying to medical image detection and segmentation.
    \end{Detail}

    \Entry
    \href{https://github.com/hackroid/pMOEA-D}
    {\textbf{Parallel Implementation of MOEA/D and its Application to Feature Selection} [link to GitHub]}
    % \Gap
    \BulletItem
    Undergraduate Project, SUSTech, Supervisor: \href{https://hisaolab-sustech.github.io/}{Prof.~Hisao~Ishibuchi}
    \hfill
    \DatestampYMD{2018}{09}{01} --
    \DatestampYMD{2019}{06}{01}
    \begin{Detail}
        \SubBulletItem
        Languages: Python, MATLAB
        \SubBulletItem
        Summary:
        This project aims to parallelize MOEA/D by using the island model and find out an effective way in which partial data would be used for communication. Several feature selection cases are used for verification.
    \end{Detail}


    %%%%%%%%%%%%%%%%%%%%%
    %% WORK EXPERIENCE %%
    %%%%%%%%%%%%%%%%%%%%%

    \Section
    {Work\newline
        Experience}
    {Work Experience}
    {PDF:WorkExperience}

    \Entry
    \href{https://tech.pingan.com/}
    {\textbf{Ping An Technology}},
    Shenzhen, Guangdong, China

    % \Gap
    \BulletItem
    Development Intern,
    Knowledge Graph Dev Team
    \hfill
    \DatestampYMD{2020}{06}{15} --
    \DatestampYMD{2020}{11}{06}
    \begin{Detail}
        \SubBulletItem
        Django back-end development: our team collaborates to run a stock recommendation system. I am responsible for designing and maintaining the back-end API to provide specific forms of information based on team members' requirements. The team's requirements are often extremely complex and require basic stock data engineering knowledge to understand, but meanwhile, it's highly modular. I designed an abstract calculation syntax tree to handle the information that team members have preliminarily processed.
    \end{Detail}


    %%%%%%%%%%%%%%%%%%%%%%
    %%  COURSE PROJECTS %%
    %%%%%%%%%%%%%%%%%%%%%%

    \Section
    {Course \newline
        Projects}
    {Course Projects}
    {PDF:CourseProjects}

    \BulletItem
    \href{https://github.com/hackroid/6.824-2023sp}{\textbf{KVRaft: Labs of 6.824 Distributed Systems} [link to Github]}
    \hfill
    \DatestampYMD{2023}{01}{01} -- Present
    % \DatestampYMD{2019}{06}{01}
    \begin{Detail}
        \SubBulletItem
        This 4 labs aim to develop a sharded, fault-tolerant, and distributed key-value store service on clusters. Whole project is written in golang as my introductory study of golang.
    \end{Detail}

    \Gap

    \BulletItem
    \href{https://github.com/hackroid/snappat}{\textbf{Snappat -- A social network app based on puzzles} [link to Github]}
    \hfill
    \DatestampYMD{2019}{02}{01} --
    \DatestampYMD{2019}{06}{01}
    \begin{Detail}
        \SubBulletItem
        This project aims to develop a social networking app covering several features like social function, machine learning, object recognition, and puzzle solving.
        \SubBulletItem
        In charge for: entire app UML design, homepage/fragment card development, code version management.
    \end{Detail}

    \Gap

    \BulletItem
    \href{https://github.com/hackroid/MqttSensorDemo}{\textbf{Sensor Data Real Time Transmission Application} [link to GitHub]}
    \hfill
    \DatestampYMD{2018}{09}{01} --
    \DatestampYMD{2019}{01}{01}
    \begin{Detail}
        \SubBulletItem
        Building an Android app to send the sensor's data between multi-device using MQTT protocol.
        \SubBulletItem
        In charge for: entire android app development and MQTT server maintenance.
    \end{Detail}

    \Gap

    \BulletItem
    \href{https://github.com/zhaoweizhong/Faculty-Reservation}{\textbf{Faculty Reservation System} [link to GitHub]}
    \hfill
    \DatestampYMD{2018}{09}{01} --
    \DatestampYMD{2019}{01}{01}
    \begin{Detail}
        \SubBulletItem
        This project is to develop a system for helping SUSTech students and faculty schedule their meetings. The system covers several important features, such as user registration, user information, and appointment scheduling.
        \SubBulletItem
        In charge for: PHP back-end spider development for grabbing data from researchgate.
    \end{Detail}

    % \Gap

    % \BulletItem
    % \href{https://github.com/hackroid/Mr.Earthquake}{\textbf{Earthquake Visualization Software} [link to GitHub]}
    % \hfill
    % \DatestampYMD{2017}{02}{01} --
    % \DatestampYMD{2017}{06}{01}
    % \begin{Detail}
    %     \SubBulletItem Developing a software which performed visualized and statistical seismal data using Java GUI.
    %     \SubBulletItem In charge for: Java back-end spider for grabbing seismal data from web.
    % \end{Detail}

    \Gap

    \BulletItem
    \textbf{Flight Reservation System}
    \hfill
    \DatestampYMD{2016}{09}{01} --
    \DatestampYMD{2017}{01}{01}
    \begin{Detail}
        \SubBulletItem Developing an online flight reservation system by JSP and JavaBean including functions like user registration, flight querying, flight reservation, flight management.
        \SubBulletItem In charge for: full-stack development including JSP web pages, material designed frontend, MySQL databases.
    \end{Detail}

    \Gap

    \BulletItem
    \textbf{Remarks}
    \begin{Detail}
        \Item
        Last 4 projects of above are course projects (in SUSTech) of: software engineering, computer network, object-oriented analysis and design, advanced java programming course, respectively.
    \end{Detail}

    % Manual page break.
    %newpage


    %%%%%%%%%%%%%%%%%%%%%%%%%%%
    %% AWARDS & SCHOLARSHIPS %%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%

    % \Section
    % {Awards \&\newline
    %     Scholarships}
    % {Awards \& Scholarships}
    % {PDF:AwardsAndScholarships}

    % \BulletItem
    % \textbf{Best Student Assistant},
    % Shuren College,
    % SUSTech
    % \hfill
    % \DatestampYMD{2016}{09}{01} --
    % \DatestampYMD{2018}{06}{01}
    % \begin{Detail}
    %     \Item
    %     Awarded to the outstanding student assistants for helping tutors and students with college affairs.
    % \end{Detail}

    % \Gap
    % \BulletItem
    % \textbf{Undergraduate Scholarship},
    % SUSTech
    % \hfill
    % \DatestampYMD{2016}{09}{01}
    % \begin{Detail}
    %     \Item
    %     Awarded to the top students at the beginning of the undergraduate.
    % \end{Detail}

    % Manual page break.
    %newpage

    %%%%%%%%%%%%%%%%%%%%%%%
    %% CAMPUS ACTIVITIES %%
    %%%%%%%%%%%%%%%%%%%%%%%

    % \Section
    % {Campus Activities}
    % {Campus Activities}
    % {PDF:CampusActivities}

    % \Entry
    % \href{https://www.sustech.edu.cn/en/campus-life.html?lang=en}
    % {\textbf{Student Congress}},
    % SUSTech

    % \Gap
    % \BulletItem
    % Representative
    % \hfill
    % \DatestampYMD{2016}{09}{01} --
    % \DatestampYMD{2020}{07}{01}
    % \begin{Detail}
    %     \SubBulletItem
    %     Participate in making important decisions about student affairs.
    % \end{Detail}


    %%%%%%%%%%%%
    %% SKILLS %%
    %%%%%%%%%%%%

    \Section
    {Skills}
    {Skills}
    {PDF:Skills}

    \Entry
    \BulletItem
    % {\color{black} $\varheart$} Python,
    Python (advanced),
    Go,
    C/C++,
    Java,
    SQL,
    Shell,
    {\LaTeX}
    % \BulletItem
    % Adobe Photoshop,
    % Adobe Premiere Pro,


    %%%%%%%%%%%%%%%
    %% LANGUAGES %%
    %%%%%%%%%%%%%%%

    \Section
    {Languages}
    {Languages}
    {PDF:Languages}

    \BulletItem
    Chinese: Native \,\BulletSymbol\, English: Professional (TOEFL 84; TOEIC 885) \,\BulletSymbol\, Japanese: Basic

    % \Gap

    % \SubBulletItem
    % [\DatestampYMD{2020}{12}{06}]
    % TOEFL: 84
    % \SubBulletItem
    % [\DatestampYMD{2019}{06}{01}]
    % College English Test  (CET6): 527

    % \Gap


    %%%%%%%%%%%%%%%
    %% INTERESTS %%
    %%%%%%%%%%%%%%%

    % \Section
    % {Interests}
    % {Interests}
    % {PDF:Interests}

    % \Entry
    % Digital photography,
    % snowboarding,
    % swimming.


\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

% \BigGap
\UseNoteFont%
\null\hfill%
[\textit{\CVNote}]

\end{document}
